I can see clearly now: reinterpreting statistical significance

### 2018-10-15 main.tex
Update main.tex
Meeting with BB
Slight progress (for lots of effort)
various tweaks to ms
lots more comments on last section
put table in its own tex. Needs to be uploaded as a separate pdf
Some rearrangement:
Some hacky (meant to be quick) changes in formatting for submission to ecology
avoid PassOptionsToPackage

\documentclass[12pt, english]{wlpeerj} % Just a convenient template
\usepackage{palatino}
\usepackage{subfiles}
\usepackage[english]{babel} 
\usepackage[comma]{natbib}
\bibliographystyle{chicago2}
\usepackage{url}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{float}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{tabularx}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage[colorlinks=true, citecolor = blue, linkcolor = black]{hyperref}
\usepackage{environ}
\usepackage{marginnote}
\usepackage{lineno}
\usepackage{setspace}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\reversemarginpar
\singlespacing

\newcommand{\jd}[1]{{\bf \color{blue} JD: #1}}
\newcommand{\mk}[1]{{\bf \color{red} MK: #1}}
\newcommand{\bmb}[1]{{\bf \color{green} BMB: #1}}

\title{Is statistical significance a thing?}

\author[1]{Jonathan Dushoff}
\author[1]{Morgan P. Kain}
\author[1,2]{Ben M. Bolker?}

@@

\newpage
\singlespacing

@@

>>>>

%% https://tex.stackexchange.com/questions/238349/error-option-clash-for-package-xcolor
%% \PassOptionsToPackage{table,dvipsnames}{xcolor}
\documentclass[12pt, english, dvipsnames, table]{wlpeerj} % Just a convenient template
\usepackage{xcolor}
\definecolor{vlg}{rgb}{0.88, 0.88, 0.88}
\usepackage{palatino}
\usepackage{subfiles}
\usepackage[english]{babel} 
\usepackage[comma]{natbib}
\bibliographystyle{unsrtnat}
\usepackage{url}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{float}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{tabularx}
\usepackage{pdflscape}
\usepackage{afterpage}
\usepackage[colorlinks=true, citecolor = purple, linkcolor = purple]{hyperref}
\usepackage{environ}
\usepackage{marginnote}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{framed}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\reversemarginpar
\singlespacing
\raggedright
\parskip 0pt 
\usepackage{indentfirst}
\setlength{\parindent}{0.5cm}

%% This whole effort was a disaster!
%% \usepackage[left=2.0in]{geometry} % For reasonable spacing with todonotes
% \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
% \newcommand{\note}[2]{{\todo[linecolor=#1,backgroundcolor=#1!25,bordercolor=#1]{#2}{}}}

\newcommand{\note}[2]{{\bf \color{#1} #2}}
\newcommand{\jd}[1]{\note{blue}{JD: #1}}
\newcommand{\mk}[1]{\note{red}{MK: #1}}
\newcommand{\bmb}[1]{\note{magenta}{BMB: #1}}

\newcommand{\pval}{p-value\xspace}
\newcommand{\pvals}{p-values\xspace}
\newcommand{\citeneeded}{\textbf{CITE}}

\title{I can see clearly now: reinterpreting statistical significance}

\author[1]{Jonathan Dushoff}
\author[1]{Morgan P. Kain}
\author[1,2]{Benjamin M. Bolker}

@@

\clearpage

@@

\clearpage

\input{table.tex}

\clearpage
